\huge A Usability Evaluation of Tor Launcher

### 2016-10-21 pets2017-paper/pets2017-paper.tex
sketch out format of formative results, and add takeaway sections to formative and summative sections

\subsection{Results} 
{\color {blue}
We give a summary of all participants here!  Quotations come from live transcription and are not necessarily verbatim.

Observations in E1:

@@

The challenges users faced in the qualitative experiment and the respective underlying causes are used as feedback for redesigning the configuration interface.

@@

>>>>

\subsection{Observations and Interviews} 
{\color {blue}
We give a summary of all participants here!  Quotations come from live transcription and are not necessarily verbatim.

Observations in E1: 
\pquote{P1, NF}{summary of what they did. ``and a quote too.''}
\pquote{P2, NF}{summary of what they did. ``and a quote too.''}
\pquote{P3, NF}{summary of what they did. ``and a quote too.''}
\pquote{P4, HT}{summary of what they did. ``and a quote too.''}
\pquote{P5, UT}{summary of what they did. ``and a quote too.''}

@@

\subsection{Where Users Struggled} 
{\color {blue}
LIST `EM! 
}

@@

\subsection{Usability of Tor Launcher} 
{\color {blue}
Tell people HOW usable it seemed, based on the data.  
}
